### 2019-11-15 README.Rmd
mlr3spatiotemporal -> mlr3spatiotempcv

# mlr3spatiotemporal

Spatio-temporal extensions for mlr3.

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotemporal)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotemporal.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

| Literature Name | R Package | Reference | mlr3spatiotemporal Name |
| --------------- | --------- | --------- | ----------------------- |
| Spatial CV  | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`  |
| Spatial Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBlock`   |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVEnv`   |
| Spatial Buffering | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBuffer` |

@@

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotemporal)
library(ggplot2)

>>>>

# mlr3spatiotempcv

Spatio-temporal resampling methods for mlr3.

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotempcv.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotempcv)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotempcv.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

@@

| Literature Name | R Package | Reference | mlr3spatiotempcv Name |
| --------------- | --------- | --------- | ----------------------- |
| Spatial CV  | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`  |
| Spatial Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBlock`   |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVEnv`   |
| Spatial Buffering | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBuffer` |

@@

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotempcv)
library(ggplot2)
